---
title: "LOUISIANA EMMY PILOT ANALYTICS"
logo: assets/logo-color.svg
subtitle: "February 2026 Pilot | Week 3"
format: 
  dashboard:
    fig-dpi: 150
    theme: 
      - default
      - assets/custom_format.scss
resources:
  - assets/logo-color.svg
---

```{r}
#| label: dependencies
#| echo: false
#| warning: false

library(tidyverse)
library(emmytics)
library(here)
library(scales)
library(ggtext)
library(glitr)
library(htmltools)
```

```{r}
#| label: import
#| echo: false

df_ban <- read_rds(here("Dataout/wkly_ban.rds"))
df_duration <- read_rds(here("Dataout/wkly_duration.rds"))
df_device_origin <- read_rds(here("Dataout/wkly_device_origin.rds"))
df_dropoff <- read_rds(here("Dataout/wkly_dropoff.rds"))
```

```{r}
#| label: global_vars
#| echo: false

#identify the latest pilot
df_duration <- df_duration |> 
      dplyr::mutate(pilot = factor(pilot, unique(pilot_pds$pilot)))

# pilot_latest <- return_latest_pilot(df_duration)
pilot_latest <- "Feb 2026"

#identify the prior pilot
pilot_prior <- pilot_pds |>
  filter(state == unique(df_ban$pilot_state)) |>
  mutate(prior = lag(pilot)) |>
  filter(pilot == pilot_latest) |>
  pull()

#identify pilot week
pilot_week <- df_duration |>
  filter(pilot == pilot_latest) |>
  distinct(pilot_wk) |>
  pull() |>
  max()

pilot_week_disp <- pilot_week

# pilot_week <- -1

if (pilot_week == -1){

  pilot_week_disp <- df_duration |>
    filter(pilot == pilot_latest) |>
    distinct(pilot_wk) |>
    pull() |>
    max()

  pilot_week_disp <- str_glue("{pilot_week_disp} (cum.)")
}
```

This report documents week `r  pilot_week_disp` of the `r unique(df_ban$pilot_state)` `r pilot_latest` Emmy pilot. For the this pilot run, `r scales::label_comma()(sum(df_ban[df_ban$metric == "n_invitation",]$curr, na.rm = TRUE))` invitiations were distributed to verify income. **All data points represent values reported in week `r pilot_week_disp` and comparisions are against the same week of the `r pilot_prior` run.**

```{r}
#| label: ban_setup
#| echo: false

df_ban_wk <- df_ban |> 
    filter(pilot_wk == pilot_week)

```

## Row {height="30%"}

::: {.valuebox icon="play-circle" color="primary"}
Income Verification Started

`r df_ban_wk |> filter(denom == "applicants", metric == "n_started") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "applicants", metric == "n_started") |> pull(text_fmt)`

:::

::: {.valuebox icon="flag" color="primary"}
Completion Rate

`r df_ban_wk |> filter(denom == "applicants", metric == "share_complete") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "applicants", metric == "share_complete") |> pull(text_fmt)`

:::

::: {.valuebox icon="link-45deg" color="primary"}
Tokenized Link Share

`r df_ban_wk |> filter(denom == "events", metric == "share_tokenized") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "events", metric == "share_tokenized") |> pull(text_fmt)`

:::

::: {.valuebox icon="person-check" color="primary"}
Successful Account Logins

`r df_ban_wk |> filter(denom == "applicants", metric == "share_login_success") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "applicants", metric == "share_login_success") |> pull(text_fmt)`

:::

::: {.valuebox icon="collection" color="primary"}
Multi Employer Submissions

`r df_ban_wk |> filter(denom == "applicants", metric == "n_multi_employers") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "applicants", metric == "n_multi_employers") |> pull(text_fmt)`

:::

::: {.valuebox icon="search" color="primary"}
Missing Search Results

`r df_ban_wk |> filter(denom == "events", metric == "share_search_missing") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "events", metric == "share_search_missing") |> pull(text_fmt)`

:::

::: {.valuebox icon="share" color="primary"}
Copied Invitiation Link

`r df_ban_wk |> filter(denom == "events", metric == "n_copied_invite") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "events", metric == "n_copied_invite") |> pull(text_fmt)`

:::

<!-- ::: {.valuebox icon="exclamation-triangle" color="light"}
Errors Encountered

`r df_ban_wk |> filter(denom == "events", metric == "n_error") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "events", metric == "n_error") |> pull(text_fmt)`

::: -->



## Row 

### Column

#### Row {height = "90%"}

```{r}
#| label: viz_funnel
#| title: !expr paste0("Applicant Journey + Drop Off Rate [", pilot_latest, " Week ", pilot_week_disp, "]")
#| fig-height: 3
#| fig-wight: 10
#| 
df_dropoff |> 
  filter(pilot_wk == pilot_week) |> 
  mutate(
    event_clean_n = str_glue("{event_clean} (n = {label_number(scale_cut = cut_short_scale())(curr)})"),
    event_clean_n = fct_inorder(event_clean_n)
    ) |> 
  ggplot(aes(curr, fct_rev(event_clean_n), group = pilot_wk)) +
  geom_blank(aes(curr * 1.1)) +
  geom_col(aes(curr_lag), alpha = .3, width = .8, fill = dsac_pale_navy, na.rm = TRUE) +
  geom_errorbar(aes(xmin = curr_lag, xmax = curr_lag), color = dsac_pale_navy) +
  geom_segment(
    aes(x = curr_lag, xend = curr * 1.02), color = dsac_pale_navy, na.rm = TRUE, 
    arrow = arrow(length = unit(.2, "cm"), type = "closed")) +
  geom_col(fill = dsac_light_navy, width = .8, na.rm = TRUE) +
  # geom_errorbar(aes(xmin = prior, xmax = prior), color = "#909090") +
  geom_text(aes(x = curr_lag, label = loss_share), hjust = -.1, na.rm = TRUE, color = "#505050", family = "Source Sans 3", size = 5) +
  scale_x_continuous(label = label_number(scale_cut = cut_short_scale()), position = "top", expand = c(.005,.005)) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 18, base_family = "Source Sans 3") +
    theme(
    plot.margin = margin(4, 4, 4, 4),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
    )
```
#### Row {height = "10%"}
```{r}
#| label: viz_device
#| title: !expr paste0("Device Type [", pilot_latest, " Week ", pilot_week_disp, "]")
#| fig-height: 2
#| fig-wight: 10

df_device_origin_viz <- df_device_origin |> 
  filter(
    pilot == pilot_latest,
    pilot_wk == pilot_week
  ) 
  
 df_device_origin_viz |>
  ggplot(aes(share, as.character(pilot_wk), fill = fill_color)) +
  geom_col(width = .5) +
  geom_text(
    aes(x = lab_pos, label = lab_share, color = fill_color, 
    hjust = lab_hjust), family = "Source Sans 3", #color = "#505050",
    na.rm = TRUE
  ) +
  scale_x_continuous(limits = c(-.5, 1.5)) +
  scale_fill_identity() +
  scale_color_identity() +
  labs(x = NULL, y = NULL) +
  theme_void(base_size = 12) +
  theme(
    axis.text = element_blank(),
    plot.margin = margin(4, 4, 4, 4)
    )
```

### Column

#### Row {height="40%"}

```{r}
#| label: viz_duration
#| title: !expr paste0("Minutes to Successfully Complete Process (median + 25%-75% range) [Week ", pilot_week, "]")
#| fig-width: 25
#| fig-height: 6

df_duration |> 
  filter(
    metric == "flow_started_minutes_ago",
    pilot_wk == pilot_week) |> 
  mutate(
    fill_color = ifelse(pilot == pilot_latest, dsac_light_navy, "#707070"),
    pilot = str_glue('{pilot} (n = {label_comma()(n)})')
    ) |> 
  ggplot(aes(y = fct_rev(pilot), group = pilot, color = fill_color)) +
  geom_linerange(aes(xmin = q25, xmax = q75), linewidth = 6) +
  geom_point(aes(median), size = 15) +
  geom_text(
    aes(median, label = label_number(.1, suffix = "m")(median)), 
    family = "Source Sans 3",
     vjust = -1) +
  scale_x_continuous(label = label_number(.1, suffix = "m"), limits = c(0, NA), position = "top") +
  scale_color_identity() +
  coord_cartesian(clip = "off") + 
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 60, base_family = "Source Sans 3") +
  theme(
    strip.placement = "outside",
    strip.text = element_text(hjust = .5),
    plot.subtitle = element_markdown(),
    panel.spacing=unit(0.5, "lines"),
    plot.margin = margin(4, 4, 4, 4),
    axis.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
    )
```

#### Row

```{r}
#| label: viz_sync
#| title: !expr paste0("Sync Time with Payroll Aggregator, Seconds (median + 25%-75% range) [Week ", pilot_week_disp, "]")
#| fig-width: 20
#| fig-height: 6

df_duration |> 
  filter(
    metric == "sync_duration_seconds",
    pilot_wk == pilot_week) |>
  filter_out(is.na(employment_type)) |> 
  mutate(
    fill_color = ifelse(pilot == pilot_latest, dsac_light_navy, "#707070"),
    # pilot = str_glue('{pilot} (n = {label_comma()(n)})'),
    employment_type = str_glue('{employment_type} (n = {label_comma()(n)})')
    ) |> 
  ggplot(aes(y = employment_type, group = employment_type, color = fill_color)) +
  geom_linerange(aes(xmin = q25, xmax = q75), linewidth = 4) +
  geom_point(aes(median), size = 12) +
  geom_text(
    aes(median, label = label_number(1, suffix = "s")(median)), 
    family = "Source Sans 3", 
    vjust = -1) +
  # facet_wrap(fct_rev(pilot) ~. , strip.position = "top", scales = "free_y", ncol = 1) +
  facet_grid(fct_rev(pilot) ~. , switch = "y", scales = "free_y") +
  scale_x_continuous(label = label_number(suffix = "s"), position = "top") +
  scale_color_identity() +
  coord_cartesian(clip = "off") + 
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 40, base_family = "Source Sans 3") +
  theme(
    strip.placement = "outside",
    strip.text = element_text(hjust = .5),
    plot.subtitle = element_markdown(),
    panel.spacing=unit(0.5, "lines"),
    plot.margin = margin(4, 4, 4, 4),
    axis.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
    )
```


