---
title: "LOUISIANA EMMY PILOT ANALYTICS"
subtitle: "February 2025 Pilot | Week 2"
format: 
  dashboard:
    #fig-height: 4
    #fig-width: 6
    fig-dpi: 150
---

```{r}
#| label: dependencies
#| echo: false
#| warning: false

library(tidyverse)
library(emmytics)
library(here)
library(scales)
library(ggtext)
```

```{r}
#| label: import
#| echo: false

df_ban <- read_rds(here("Dataout/wkly_ban.rds"))
df_duration <- read_rds(here("Dataout/wkly_duration.rds"))
df_device_origin <- read_rds(here("Dataout/wkly_device_origin.rds"))
```

```{r}
#| label: global_vars
#| echo: false

#identify the latest pilot
df_duration <- df_duration |> 
      dplyr::mutate(pilot = factor(pilot, unique(pilot_pds$pilot)))

# pilot_latest <- return_latest_pilot(df_duration)
pilot_latest <- "Feb 2026"

#identify the prior pilot
pilot_prior <- pilot_pds |>
  filter(state == unique(df_ban$pilot_state)) |>
  mutate(prior = lag(pilot)) |>
  filter(pilot == pilot_latest) |>
  pull()

#identify pilot week
pilot_week <- df_duration |>
  filter(pilot == pilot_latest) |>
  distinct(pilot_wk) |>
  pull() |>
  max()

```

This report documents week `r  pilot_week` of the `r unique(df_ban$pilot_state)` `r pilot_latest` Emmy pilot. For the `r pilot_latest` run, `r scales::label_comma()(sum(df_ban[df_ban$metric == "n_invitation",]$curr, na.rm = TRUE))` invitiations were sent out. All data points represent values for week `r pilot_week` and comparisions are against `r pilot_week` week of the `r pilot_prior` run. 

```{r}
#| label: ban_setup
#| echo: false

df_ban_wk <- df_ban |> 
    filter(pilot_wk == pilot_week)

```

## Row {height="30%"}

::: {.valuebox icon="play-circle" color="light"}
Applications started

`r df_ban_wk |> filter(denom == "applicants", metric == "n_started") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "applicants", metric == "n_started") |> pull(text_fmt)`

:::

::: {.valuebox icon="flag" color="light"}
Completion Rate

`r df_ban_wk |> filter(denom == "applicants", metric == "share_complete") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "applicants", metric == "share_complete") |> pull(text_fmt)`

:::

::: {.valuebox icon="link" color="light"}
Tokenized Link Share

`r df_ban_wk |> filter(denom == "events", metric == "share_tokenized") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "events", metric == "share_tokenized") |> pull(text_fmt)`

:::

::: {.valuebox icon="binoculars" color="light"}
Missing Search Results

`r df_ban_wk |> filter(denom == "applicants", metric == "share_search_missing") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "applicants", metric == "share_search_missing") |> pull(text_fmt)`

:::

::: {.valuebox icon="question-circle" color="light"}
Number of Help Actions

`r df_ban_wk |> filter(denom == "events", metric == "n_help") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "events", metric == "n_help") |> pull(text_fmt)`

:::

::: {.valuebox icon="exclamation-circle" color="light"}
Errors Encountered

`r df_ban_wk |> filter(denom == "events", metric == "n_error") |> pull(val_fmt)`

`r df_ban_wk |> filter(denom == "events", metric == "n_error") |> pull(text_fmt)`

:::



## Row 

### Column

```{r}
#| label: viz_device
#| title: Device Type
#| fig-height: 6
#| fig-wight: 3

df_device_origin |> 
    filter(
        pilot == pilot_latest, 
        pilot_wk == pilot_week) |> 
    ggplot(aes(started, fct_reorder(str_to_title(device_type), started, sum))) +
    geom_blank(aes(x = started * 1.1)) +
    geom_col(fill = dsac_light_navy) +
    geom_text(
      aes(label = label_number(scale_cut = cut_si(""))(started)),
      hjust = -.1, color = "#505050", 
      ) +
    coord_cartesian(clip = "off") +
    labs(x = NULL, y = NULL) +
    theme_minimal(base_size = 16) +
    theme(
          plot.margin = margin(4, 4, 4, 4),
          axis.title = element_blank(),
          axis.text.x = element_blank(),
          panel.grid.minor = element_blank(),
          panel.grid.major.y = element_blank()
    )

```

### Column

#### Row {height="40%"}

```{r}
#| label: viz_duration
#| title: Time to Complete (median + IQR)
#| fig-width: 25
#| fig-height: 6

df_duration |> 
  filter(
    metric == "flow_started_minutes_ago",
    pilot_wk == pilot_week) |> 
  mutate(
    fill_color = ifelse(pilot == pilot_latest, dsac_light_navy, "#707070"),
    pilot = str_glue('{pilot} (n = {label_comma()(n)})')
    # pilot = str_glue('{pilot} | {pilot_wk}'),
    ) |> 
  ggplot(aes(y = pilot, group = pilot, color = fill_color)) +
  geom_linerange(aes(xmin = q25, xmax = q75), linewidth = 6) +
  geom_point(aes(median), size = 15) +
  geom_text(
    aes(median, label = label_number(.1, suffix = "m")(median)), 
    # family = "Source Sans 3",
     vjust = -1) +
#   facet_grid(pilot ~. , switch = "y", scales = "free_y") +
  scale_x_continuous(label = label_number(.1, suffix = "m"), limits = c(0, NA), position = "top") +
  scale_color_identity() +
  coord_cartesian(clip = "off") + 
  labs(x = NULL, y = NULL) +
#   si_style_xgrid() +
  theme_minimal(base_size = 60) +
  theme(
    strip.placement = "outside",
    strip.text = element_text(hjust = .5),
    plot.subtitle = element_markdown(),
    panel.spacing=unit(0.5, "lines"),
    plot.margin = margin(4, 4, 4, 4),
    axis.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
    )
```

#### Row

```{r}
#| label: viz_sync
#| title: Payroll Aggregator Sync Time (median + IQR)
#| fig-width: 20
#| fig-height: 6

df_duration |> 
  filter(
    metric == "sync_duration_seconds",
    pilot_wk == pilot_week) |> 
  mutate(
    fill_color = ifelse(pilot == pilot_latest, dsac_light_navy, "#707070"),
    # pilot = str_glue('{pilot} wk{pilot_wk}'),
    provider = str_glue('{provider} (n = {label_comma()(n)})')
    ) |> 
  ggplot(aes(y = fct_rev(provider), group = provider, color = fill_color)) +
  geom_linerange(aes(xmin = q25, xmax = q75), linewidth = 4) +
  geom_point(aes(median), size = 12) +
  geom_text(
    aes(median, label = label_number(1, suffix = "s")(median)), 
    # family = "Source Sans 3", 
    vjust = -1) +
  facet_grid(pilot ~. , switch = "y", scales = "free_y") +
  scale_x_continuous(label = label_number(suffix = "s"), limits = c(0, 360), position = "top") +
  scale_color_identity() +
  coord_cartesian(clip = "off") + 
  labs(x = NULL, y = NULL) +
#   si_style_xgrid() +
  theme_minimal(base_size = 40) +
  theme(
    strip.placement = "outside",
    strip.text = element_text(hjust = .5),
    plot.subtitle = element_markdown(),
    panel.spacing=unit(0.5, "lines"),
    plot.margin = margin(4, 4, 4, 4),
    axis.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
    )
```


